### 2022-09-28 chapters/optimization/python-dir/python_interperters.tex
Proofreading python

\begin{figure}[hbt]
      \includegraphics[width=.9\linewidth]{imgs/SmartWatts.png}
      \caption{Benchmarking architecture deployed with \textsc{PowerAPI}.}
      \label{fig:powerapi}
\end{figure}

@@

\begin{figure}[!htb]
      \centering
      \includegraphics[width=\linewidth]{imgs/dendogram_interpreters}
      \caption{Dendogram of the different implementations}
      \label{fig:dendogram}
\end{figure}

@@

\begin{figure}[!htb]
      \centering
      \includegraphics[height=\textheight,keepaspectratio]{imgs/alltomti_performance}
      \caption{Different interpreter's energy scores.}
      \label{fig:tommi_all}
\end{figure}

@@

As one can notice in Figure~\ref{fig:tommi_all}, there is no evolution between CPython2 and CPython3.
Moreover, IntelPython, and ActivePython all behave similarly to the reference implementation.
Therefore, one can conclude that the work done on those interpreters is primarily to improve a specific purpose, not the core interpreter.
ActivePython states that its version is focused on security and prepackaged libraries, which explains why it is slower than other versions due to the addition of this security support.\footnote{\url{https://www.activestate.com/solutions/why-activestate/}}
As for IntelPython, it is designed for machine learning.
Unfortunately, the \textsc{Tommti} benchmark is geared for general-purpose programming.
Although Nuitxka is a compiler, there was no discernible difference in energy consumption.
It was even more similar to the reference Python implementation than other interpreters.
However, looking at the Nuitka techniques, we can see that they simply encapsulate the Python code with an interpreter into a single executable.
Finally, Shedskin reports on the best energy consumption pattern in arithmetic operations.
One can conclude it is due to the native type of the variables, unlike in the JIT, where they are treated as objects initially.

@@

\subsubsection{threads to validity }
Due to the lack of support for most non-conventional Python interpreters, we mainly focus on micro-benchmarks.
Except for \textsc{PyPy}, most of the Python implementations do not support extra Python libraries, despite those different implementations being developed to optimize a specific library, such as \textsf{Numba} with \textsf{Numpy}, or \textsf{intelpython} with machine learning algorithms.
Furthermore, we excluded from this study runtime that could not complete our benchmarks because we judged that this was the bare minimum for an implementation to be employed in a real-world application.
Besides this, since the goal of this study was to provide a non-intrusive technique to decrease the energy consumption of software, we opted to omit some of the implementations that required extra work on the source code to run on them, such as \textsf{Cython}.

\subsection{Conclusion}

One can conclude that the Python interpreter used considerably impacts the programs' energy consumption. Furthermore, the absence of a universal solution makes this investigation more intriguing.
While most of the candidates employed Python2, Python3 provided better compatibility coverage.
Except for Pypy, a standout interpreter, the optimization strategy substantially impacted energy usage because each class was grouped regardless of the Python version.
Finally, JIT, a technology that converts code into machine code at runtime, was responsible for the significant gain in energy efficiency. The usage of translators such as Shedskin confirmed the effect of compiling Python code into machine code. Hence, PyPy, an interpreter with a built-in JIT, is within the same class as the complied ones, such as Shedskin.

>>>>

\begin{figure}[hbt]
      \centering
      \includegraphics[width=.8\linewidth]{imgs/SmartWatts.png}
      \caption{Benchmarking architecture deployed with \textsc{PowerAPI}.}
      \label{fig:powerapi}
\end{figure}

@@

\begin{figure}[!htb]
      \centering
      \includegraphics[width=.8\linewidth]{imgs/dendogram_interpreters}
      \caption{Dendogram of the different Python runtime implementations.}
      \label{fig:dendogram}
\end{figure}

@@

\begin{figure}[!htb]
      \centering
      \includegraphics[height=\textheight,keepaspectratio]{imgs/alltomti_performance}
      \caption{Different Python runtime energy scores.}
      \label{fig:tommi_all}
\end{figure}

@@

As one can notice in Figure~\ref{fig:tommi_all}, there is no evolution between CPython2 and CPython3.
Moreover, IntelPython, and ActivePython all behave similarly to the reference implementation.
Therefore, one can conclude that the work done on those interpreters is primarily to improve a specific purpose, not the core interpreter.
ActivePython states that its version is focused on security and prepackaged libraries, which explains why it is slower than other versions due to the addition of this security support.\footnote{\url{https://www.activestate.com/solutions/why-activestate/}}
As for IntelPython, it is designed for machine learning.
Unfortunately, the \textsc{Tommti} benchmark is geared for general-purpose programming.
Although Nuitka is a compiler, there was no discernible difference in energy consumption.
It was even more similar to the reference Python implementation than other interpreters.
However, looking at the Nuitka techniques, we can see that they simply encapsulate the Python code with an interpreter into a single executable.
Finally, Shedskin reports on the best energy consumption pattern in arithmetic operations.
One can conclude it is due to the native type of the variables, unlike in the JIT, where they are treated as objects initially.

@@

\subsubsection{Threats to validity}
Due to the lack of support for most non-conventional Python interpreters, we mainly focus on micro-benchmarks.
Except for \textsc{PyPy}, most of the Python implementations do not support extra Python libraries, despite those different implementations being developed to optimize a specific library, such as \textsf{Numba} with \textsf{Numpy}, or \textsf{IntelPython} with machine learning algorithms.
Furthermore, we excluded from this study runtime that could not complete our benchmarks because we judged that this was the bare minimum for an implementation to be employed in a real-world application.
Besides this, since the goal of this study was to provide a non-intrusive technique to decrease the energy consumption of software, we opted to omit some of the implementations that required extra work on the source code to run on them, such as \textsf{Cython}.

\subsection{Conclusion}
One can conclude that the Python interpreter used considerably impacts the programs' energy consumption.
Furthermore, the absence of a universal solution makes this investigation more intriguing.
While most of the candidates employed \textsf{Python2}, \textsf{Python3} provided better compatibility coverage.
Except for \textsf{Pypy}, a standout interpreter, the optimization strategy substantially impacted energy usage because each class was grouped regardless of the Python version.
Finally, JIT, a technology that converts code into machine code at runtime, was responsible for the significant gain in energy efficiency.
The usage of translators, such as \textsf{Shedskin} confirmed the effect of compiling Python code into machine code. Hence, \textsf{PyPy}, an interpreter with a built-in JIT, is within the same class as the complied ones, such as \textsf{Shedskin}.
